An Instance Based Reasoning for Empirical Transfer Learning

### 2015-04-08 manuscript.tex
results

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{tabulary}
\usepackage{bigstrut}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\usepackage{picture}
\newcommand{\keyword}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(100,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

In addition to the above, we rank the different variants of the planning scheme to identify the best approach. We make use of the Scott-Knott procedure, recommended by \cite{} to compute the ranks. It works as follows: A list of treatments \textit{l} is sorted by the median score. The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division. A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different. If so, Skott-Knott then recurses on each division. In our paper, we use the A12 test and a non-parametric bootstrap sampling for hypothesis testing. 
% \section{Experimental Results}
% \section{Discussion}
% \section{Threats to validity}
% \section{Conclusion}
% \section*{Acknowledgements}
%\begin{thebibliography}{10}
%\bibitem{test}
%\end{thebibliography}
\end{document}

>>>>

 \documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{tabulary}
\usepackage{bigstrut}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.9}
\usepackage{picture}
\newcommand{\keyword}[1]{\textit{#1}}
\newcommand{\quart}[4]{\begin{picture}(100,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

@@

In addition to the above, we rank the different variants of the planning scheme to identify the best approach. We make use of the Scott-Knott procedure, recommended by \cite{} to compute the ranks. It works as follows: A list of treatments \textit{l} is sorted by the median score. The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division. A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different. If so, Skott-Knott then recurses on each division. In our paper, we use the A12 test and a non-parametric bootstrap sampling for hypothesis testing. 
\section{Experimental Results}
\begin{figure}[!t]

\begin{minipage}{0.5\textwidth}
\renewcommand{\baselinestretch}{}
{\bf \scriptsize Ant:}

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
    \hline  2 & $\alpha=0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
    \hline  4 &     $\alpha=0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
    4 &   $\alpha=0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
    4 & $\alpha=0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
    \hline  5 &    $\alpha=0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
    5 &      $\alpha=0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
    \hline  6 &     $\alpha=0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
    6 &   $\alpha=0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
    \hline \end{tabular}\\}

{\bf \scriptsize Camel}

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
1 &   $\alpha=0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
1 & $\alpha=0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
\hline  2 & $\alpha=0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
\hline  3 &    $\alpha=0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
3 &  $\alpha=0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
\hline  4 & $\alpha=0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
\hline  5 & $\alpha=0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
5 &   $\alpha=0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
\hline  6 & $\alpha=0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
\hline \end{tabular}}\\

{\bf \scriptsize Ivy}

    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
        \arrayrulecolor{darkgray}
        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
        \hline  2 & $\alpha=0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
        \hline  3 & $\alpha=0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
        \hline  4 & $\alpha=0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
        \hline  5 &     $\alpha=0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
        5 &   $\alpha=0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
        \hline  6 &    $\alpha=0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
        6 &      $\alpha=0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
        \hline  7 &   $\alpha=0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
        7 &     $\alpha=0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
        \hline \end{tabular}}\\

{\bf \scriptsize Jedit}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
      \hline  2 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
      \hline  3 & $\alpha=0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
      \hline  4 &   $\alpha=0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
      4 & $\alpha=0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
      \hline  5 & $\alpha=0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
      5 &  $\alpha=0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
      5 &    $\alpha=0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
      \hline  6 &   $\alpha=0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
      6 & $\alpha=0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
      \hline \end{tabular}}\\
\end{minipage}
\end{figure}
\begin{figure}
\begin{minipage}{0.5\textwidth}
  \renewcommand{\baselinestretch}{}
{\bf \scriptsize Log4j}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
      1 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
      1 & $\alpha=0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
      1 &  $\alpha=0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
      1 &   $\alpha=0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
      \hline  2 &    $\alpha=0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
      2 & $\alpha=0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
      2 & $\alpha=0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
      2 &   $\alpha=0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
      \hline \end{tabular}}\\

{\bf \scriptsize Lucene}

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $\alpha=0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
    1 &  $\alpha=0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
    \hline  2 &   $\alpha=0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
    2 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
    2 & $\alpha=0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
    \hline  4 & $\alpha=0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
    4 &  $\alpha=0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
    4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\

{\bf \scriptsize Poi}

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
    1 & $\alpha=0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
    \hline  2 &     $\alpha=0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
    2 &   $\alpha=0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
    \hline  3 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
    3 &    $\alpha=0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
    \hline  4 &     $\alpha=0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
    4 &      $\alpha=0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
    4 &   $\alpha=0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
    \hline \end{tabular}}  \\

{\bf \scriptsize Velocity}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
      1 & $\alpha=0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
      \hline  3 & $\alpha=0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
      3 & $\alpha=0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
      3 & $\alpha=0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
      \hline  4 & $\alpha=0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
      4 & $\alpha=0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
      4 & $\alpha=0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
      4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
      \hline \end{tabular}}\\

{\bf \scriptsize Xalan}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
      1 & $\alpha=0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
      1 &   $\alpha=0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
      \hline  2 &    $\alpha=0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
      2 &  $\alpha=0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
      2 & $\alpha=0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
      2 & $\alpha=0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
      2 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
      2 &   $\alpha=0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
      \hline \end{tabular}}
 \end{minipage}  
   \end{figure}

% \section{Discussion}
% \section{Threats to validity}
% \section{Conclusion}
% \section*{Acknowledgements}
%\begin{thebibliography}{10}
%\bibitem{test}
%\end{thebibliography}
\end{document}
